Digging Deeper Into the State of the Practice for Domain Specific Research Software

### 2022-02-18 StateOfPractice/Papers/ICCS-2022-SOP_MethodologyPlusExamples/DigDeep.tex
Changed link to data to Memdeley dataset

Figure~\ref{Fig_OverallScore} shows the overall ranking of the LBM software
packages. In the absence of other information on priorities, the overall ranking
was calculated by assuming an equal weighting between all qualities.  The LBM data is available \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/DomainMeasurements/LBM-Peter/Completed_LBS_Combined_MeasurementTemplate_EmpiricalMeasures_ADDED_MUSUBI_UPDATED_STATS.xlsx} {on-line}.

>>>>

Figure~\ref{Fig_OverallScore} shows the overall ranking of the LBM software
packages. In the absence of other information on priorities, the overall ranking
was calculated by assuming an equal weighting between all qualities.  The LBM data is available \href{https://data.mendeley.com/datasets/5dym63wn6z/1} {on-line}.
